An effective sensor grid approach for large scale acoustic monitoring

### 2017-06-14 paper/article.tex
scketching intro

\title{An efficient audio coding scheme for large scale acoustic monitoring}

@@

>>>>

\title{An effective sensor grid approach for large scale acoustic monitoring}

@@

As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.

The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.

requirements

scalability:
power managment:
security and privacy:
data richness:

low consumption computation (processing and transmission) of the sensor node

low bitrate of the transmitted data for efficient transmission and storage

proposed approach

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figures/censeCoder}
\vspace{-0.15in}
\caption{}
\label{fig:codingScheme}
\end{figure}
